Adopting agile in the large: motivations, success factors and challenges

### 2014-05-13 journal/article.tex
Long term planning

>>>>

% Long term planning

High level requirements work and estimation was problematic as there was a gap
between short and long term planning [P9, P10]. Typical agile backlogs would
give only short term visibility, so organization specific practices for business
to do long term planning had to be created [P26, P31]. Several cases described
that care had to be taken to avoid long term planning becoming a prescriptive
practice. In order to preserve the agility of development a schedule driven
approach was avoided [P10], sensitivity was used when considering setting
milestones [P13], and striving for more accurate estimates was not let to become
an excuse for gathering requirements up front [P38].
